The Inner Mass-Ratio Distribution of Intermediate-Mass Stars

### 2016-02-05 paper/ms.tex
Removed some stars with detections I do not believe.
Added CCF figure for demonstration purposes.

We list the companion detections in Table \ref{tab:companions}, and report the estimate of the companion temperature, $v\sin{i}$, and metallicity derived from the model parameters which produce the largest CCF peak. The $v\sin{i}$ and metallicity values do not have uncertainties and should only be taken as a rough estimate of the true value.

TODO: Make plots for all of the CCFs.

Most of the detected companions have follow-up spectra to confirm the existence of the companion. [MENTION THAT YOU CAN SEE THEM ALL IN THE FIGURES]. In most cases, there is a clear shift in the radial velocity of the companion, indicating that it is orbiting the target star and is not a foreground or background companion. In addition we obtained Gemini/NIRI adaptive optics imaging data for 19 of the northern companions, and were able to resolve 7 of them.

@@

We do not use systems with more than one companion, unless the wider companion is separated by $ > 10''$ from the primary star. We mark the 48 companions we use in the mass ratio analysis with the fourth column of Table \ref{tab:companions}. Many of the companions we use in the analysis only have one detection in our data; 12/22 of these are previously known companions and so don't need follow-up to confirm. The remaining 10 are new and unconfirmed detections; these all have very strong CCF signals and are likely to be confirmed with follow-up spectroscopy or imaging. We do not expect their inclusion to significantly alter the results. TODO: test this statement...

@@

    HIP 5348 &        B6V+B9V &    01:08:23.08 &   -55:14:44.73 &  6325.56 &     CHIRON &      186 &   390 \\

@@

  HIP 12332 & AB$^{\dagger}$ &     2 & yes &  $5551 \pm 107$ &      10 &     0.0  &    $1.0^{+0.03}_{--0.03}$ &  $1.0^{+0.01}_{-0.04}$ \\

@@

  HIP 14764 & AB$^{\dagger}$ &     2 & yes &  $5601 \pm 108$ &      30 &     0.5 0 &    $1.0^{+0.34}_{-0.05}$ &  $1.0^{+0.03}_{-0.03}$ \\

@@

  HIP 16611 & AB &     1 & no &  $5476 \pm 154$ &       1 &     0.5  &  $0.9^{+0.04}_{-0.04}$ &  $0.9^{+0.04}_{-0.03}$ \\
  HIP 17563 & AB &     1 & yes &  $8574 \pm 147$ &       5 &     0.5  &  $1.9^{+0.25}_{-0.11}$ &  $2.0^{+0.05}_{-0.06}$ \\

@@

  HIP 22958 & Aa,Ab &     2 & yes &  $6126 \pm 112$ &      30 &    -0.5  &  $1.4^{+0.22}_{-0.21}$ &  $1.2^{+0.04}_{-0.04}$ \\

@@

  HIP 25143 & AB$^{\dagger}$ &     2 & yes &  $5883 \pm 109$ &      30 &     0.0  &  $1.1^{+0.04}_{-0.03}$ &  $1.1^{+0.05}_{-0.07}$ \\

@@

  HIP 16611 &   $12514 \pm 425$ &  $4.0 \pm 0.14$ &  $3.3^{+0.25}_{-0.20}$ &    $157^{+23}_{-46}$ &      DH2015 \\
  HIP 17563 &  $19000 \pm 1000$ &  $4.5 \pm 0.25$ &  $6.0^{+0.66}_{-0.59}$ &      $10^{+11}_{-4}$ &  This Study \\

@@

  HIP 25143 &    $8101 \pm 275$ &  $3.8 \pm 0.14$ &  $1.7^{+0.06}_{-0.06}$ &  $236^{+247}_{-160}$ &      DH2015 \\

>>>>

We list the companion detections in Table \ref{tab:companions}, and report the estimate of the companion temperature, $v\sin{i}$, and metallicity derived from the model parameters which produce the largest CCF peak. The $v\sin{i}$ and metallicity values do not have uncertainties and should only be taken as a rough estimate of the true value. We show the detection CCFs and a plot of peak CCF height as a function of model temperature in Figure \ref{fig:ccf}. Similar figures for all companions are available in the supplementary files.

\begin{figure}
\includegraphics[width=\pagewidth]{HIP_109139.pdf}
\caption{\emph{Left}: Cross-correlation function between the observed spectra of HIP 109139 and a $5700\ K$ Phoenix model spectra. The detection at two dates shows significant velocity variation, indicating orbital motion with a short period. \emph{Right}: Peak CCF height as a function of Phoenix model spectra template temperature. The maxima of the curves indicate the temperature of the companion.}
\label{fig:ccf}
\end{figure}

Most of the detected companions have follow-up spectra to confirm the existence of the companion. In most cases, there is a clear shift in the radial velocity of the companion, indicating that it is orbiting the target star and is not a foreground or background companion. In addition we obtained Gemini/NIRI adaptive optics imaging data for 19 of the northern companions, and were able to resolve 7 of them. We show the separation, position angle, and magnitude difference in Table \ref{tab:imaging_obs}.

@@

We do not use systems with more than one companion, unless the wider companion is separated by $ > 10''$ from the primary star. We mark the 48 companions we use in the mass ratio analysis with the fourth column of Table \ref{tab:companions}. Many of the companions we use in the analysis only have one detection in our data; 12/22 of these are previously known companions and so don't need follow-up to confirm. An The remaining 10 are new and unconfirmed detections; these all have very strong CCF signals and are likely to be confirmed with follow-up spectroscopy or imaging. We do not expect their inclusion to significantly alter the results. TODO: test this statement...

Where did HIP 118243 go? It has an imaging detection (though at very wide separation), but nothing in the Companion table.

@@

@@

  HIP 12332 & AB$^{\dagger}$ &     2 & yes &  $5551 \pm 107$ &      10 &     0.0  &    $1.0^{+0.03}_{-0.03}$ &  $1.0^{+0.01}_{-0.04}$ \\

@@

  HIP 14764 & AB$^{\dagger}$ &     2 & yes &  $5623 \pm 150$ &      5 &     -0.5 &    $1.0^{+0.32}_{-0.07}$ &  $1.0^{+0.03}_{-0.04}$ \\

@@

@@

  HIP 22958 & Aa,Ab &     2 & yes &  $5762 \pm 158$ &      30 &    -0.5  &  $1.3^{+0.19}_{-0.23}$ &  $1.0^{+0.09}_{-0.03}$ \\

@@

@@

@@
